---
title: "DY6 Recruitment"
output: html_notebook
---

```{r message=FALSE}
# Load packages
library(tidyverse)
library(odbc)

# Load functions
about_data <- function(x) {
  cat(nrow(x), "observations and", length(x), "variables in the data \n")
}

dup_ids <- function(x) {
  dups <- duplicated(x)
  ids <- x[dups]
  cat("There are", sum(dups), "duplicate ID's \n")
  cat("Duplicate ID's: \n")
  print(ids)
}
```

# Connect to CCM database

```{r}
# con <- DBI::dbConnect(odbc::odbc(),
#                       driver = "ODBC Driver 13 for SQL Server",
#                       server = "10.10.1.198",
#                       database = "Navigator_UNT",
#                       uid = "CCMRPT_UNT",
#                       pwd = "Tasewe-E3recUBRE")
```

# View available tables

```{r}
# tables_look<-dbListTables(con, schema="lookup")
# tables_dbo<-dbListTables(con, schema="dbo")
```

# Read in needed data

```{r}
# table <- tables_dbo[48]
# query <- paste("SELECT * FROM", table)
# df <- dbFetch((dbSendQuery(con, query)))
```

```{r}
# dbExistsTable(con, "HomeHealthOasisQuestion")
```

# Close the connection

```{r}
# dbDisconnect(con) 
```

Not currently working. However, Doug already imported this data and saved it as a CSV file. I'll come back to connecting to the database at some point. For now, just get recruitment numbers from the CSV file.

# Load data

```{r message=FALSE}
# Read in data
df <- read_csv(file = "../data/dbo_CSV/HomeHealthOasisQuestion.csv")

# Convert date columns from type character to type date
# Select date columns
dates <- c("dc_str", "hosp_dc_date", "soc_str", "tm_start", "tm_stop", "ns_intervention_str")

# Make the conversion and overwrite the data
df <- df %>% 
  mutate(ContactDate = as.Date(df$ContactDate)) %>% 
  map_at(dates, ~ as.Date(., format = "%m/%d/%Y")) %>% 
  as_tibble()

about_data(df) # 2226 observations and 25 variables in the data
```

How many unique people?

```{r echo=FALSE}
df$PatientId %>% unique() %>% length() # 666
```

This data is current as of:

```{r echo=FALSE}
max(df$soc_str, na.rm = TRUE) # "2017-04-08"
```

-----

# Calculate enrollment

## Only keep rows with m0100 = 1

```{r}
# m0100: This assessment is currently being completed for the following reason:
df$m0100 <- factor(df$m0100,
  levels = c(1, 8, 9),
  labels = c("Start of care", "Death at home", "Discharge"))
```

## Sort by patient id

```{r}
df <- df %>% arrange(PatientId, soc_str)
```

## Keep only 1's from M0100 (start of care)

```{r}
df <- filter(df, m0100 == "Start of care")
about_data(df) # 685 observations and 25 variables in the data
```

# Enrollment

* For enrollment purposes, 2016-10-01 is the magic day for DY6 - even though we actually hit 400 before that date.
 
* Individuals with a start of care date prior to 2016-10-01, who were discharged from services on or after 2016-10-01, are considered rollover patients.
 
* Individuals with a start of care data on or after 2016-10-01 are DY6 (non-rollover) enrollments.

## How many people were actively enrolled on 2016-10-01 (rollovers)?

```{r}
rollovers <- df %>% 
  filter(soc_str < "2016-10-01" & (dc_str >= "2016-10-01" | is.na(dc_str)))

about_data(rollovers) # 234 observations and 25 variables in the data 
```

### How many of these are duplicates?

```{r}
dups <- dup_ids(rollovers$PatientId)
```

```{r}
rollovers %>% filter(PatientId %in% dups)
```
&nbsp;

I will email CCM to get clarification on which row to keep.

## How many people were newly enrolled on or after 2016-10-01?

```{r}
dy6_new <- df %>% 
  filter(soc_str >= "2016-10-01")

about_data(dy6_new) # 123 observations and 25 variables in the data  
```

## Append the rollovers and the new admits

```{r}
dy6 <- bind_rows(rollovers, dy6_new)
```

## Check for duplicates

```{r}
dups <- dup_ids(dy6$PatientId)
```
&nbsp;

I will email CCM to get clarification on which row to keep.

```{r}
dy6 %>% distinct(PatientId) %>% nrow() # 356
```
&nbsp;

Are any enrolled outside of the 14-day window?

```{r}
dy6 %>% filter(days_since_hosp_dc > 14 | is.na(days_since_hosp_dc)) %>% nrow() # 1
```

```{r}
dy6 %>% filter(days_since_hosp_dc > 14 | is.na(days_since_hosp_dc))
```


# Enrollment Summary

There were 233 people (234 observations) that were enrolled before 2016-10-01, and were discharged on or after 2016-10-01. These are rollover patients.

There were an additional 123 people with a start of care date on or after 2016-10-01. These people are new enrollments within DY6

As of this report, there are 356 DY6 enrollments.

However, one person (15379) may not count because of enrollment outside the 14-day window. That brings the new count to 355.

All 355 people have only one DY6 enrollment. However, they may have a previous enrollment in other DY's. This is allowed.

All 355 people were enrolled within 14 days of hospital discharge.


-------------------------------------------------------------------------------

&nbsp;

#### Session Info:

```{r session_info, echo=FALSE}
sessionInfo()
```