---
title: "ICD 10 to ICD 9 codes"
output: html_document
---

```{r}
library(tidyverse)
library(bfuncs)
library(icd)
```
#Import ICD key

https://www.icd10data.com/ICD10CM/Index Contains Index of all ICD10 codes for reference

http://icd10cmcode.com/icd9to10conversion.php Good Resource to show that there are some instances where one ICD-9 code may equate to multiple ICD-10 codes and vice versa.

All other ICD10 to ICD9 converter files you have to pay for.  For the codes I have plugged into online translator websites, this key seems to be accurate.

```{r}
key <- readxl::read_excel("/Volumes/sph_research/Waiver Evaluation/Old icd stuff/ICD10 to ICD9 Bridge File.xlsx")
```
#Import Waiver Patient Data w/ ICD codes

```{r}
waiver_patients <- read.csv("/Volumes/sph_research/Waiver Evaluation/dbo_CSV/PatientDiagnosis.csv")
```

```{r}
about_data(waiver_patients) #13134 observations, 10 variables
```


#Join ICD9 codes to waiver_patients

```{r}
colnames(waiver_patients)[colnames(waiver_patients)=="Code"] <- "ICD10"
```


```{r}
waiver_patients_icd9 <- waiver_patients %>%
  left_join(key, by = "ICD10") %>%
  print()
```

```{r}
about_data(waiver_patients_icd9) #17089 observations, 11 variables
```
Number of observations increased because there are instances where one ICD10 code corresponds to multiple ICD9 codes.



#Import Control Data

```{r}
control_patients <- readxl::read_excel("/Volumes/sph_research/Waiver Evaluation/UNTHSC Final W Admit Dt.xlsx")
```

```{r}
about_data(control_patients) #18695 observations and 17 variables
```

#Join ICD9 codes to control_patients

Key ICD codes include decimal points, control patient ICD codes do not include decimal places.

##Removing Decimal Places from Key
```{r}
key <- toString(as.matrix(key))
```

```{r}
key <- str_remove_all(as.matrix(key), "[.]")
```

```{r}
colnames(control_patients)[colnames(control_patients)=="ADMIT_DX"] <- "ICD10"
```


##Joining New Key to control_patients
```{r}
control_patients_icd9 <- control_patients %>%
  left_join(key, by = "ICD10") %>%
  print()
```
This doesn't work because now key is not a data frame.

```{r}
key <- data_frame(key)
```




