---
title: "Analyze Waiver Data (No Control Group)"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(plyr)
library(dplyr)
library(stargazer)
```


## Data Manipulation
Set unknowns to missing and collapse categories for easier interpretation 

```{r }

setwd("C:\\Users\\mdl0193\\Dropbox\\RF9987 - 1115 Waiver Managing Chronically Ill Medicaid Patients Using Interventional Telehealth\\waiverEvaluation\\R")

#read raw data and clean any discrepancies
analyze<-read.csv("WaiverAnalyze.csv")
analyze<-mutate(analyze, time_till=ifelse(time_till<0, NA, time_till))
analyze<-mutate(analyze, Gender=ifelse(Gender=="U", NA, Gender))

#recategorize
analyze<-mutate(analyze, Male=as.numeric(revalue(as.character(Gender), c('2'='1', '1'='0'))))
analyze<-mutate(analyze, White=ifelse(Race=="Caucasian", 1, 0))
analyze<-mutate(analyze, Partner=revalue(MaritalStatus, c("Divorced"="No","Life Partner"="Yes","Married"="Yes","Separated"="No","Single"="No","Unknown"=NA,"Widowed"="No")))
analyze$inpatient<-factor(analyze$inpatient,levels=c(0,1),labels=c("No","Yes"))
```

## Logistic Regressions 
OR and CIs predicting an inpatient hospitilization 
Only significant effect is time between discharge and TM start, but in the opposite of the theorized direction. Is it possible that "healthier" patients were less prioritized for TM start?

Same pattern seen in results for ER visits
```{r}
attach(analyze)
  
  mylogit<-glm(inpatient~Male,family="binomial")
  exp(cbind(OR = coef(mylogit), confint(mylogit)))
  
  mylogit<-glm(inpatient~White,family="binomial")
  exp(cbind(OR = coef(mylogit), confint(mylogit)))
  
   mylogit<-glm(inpatient~Partner,family="binomial")
  exp(cbind(OR = coef(mylogit), confint(mylogit)))
  

  mylogit<-glm(inpatient~time_till,family="binomial")
  exp(cbind(OR = coef(mylogit), confint(mylogit)))
  
  mylogit<-glm(inpatient~age,family="binomial")
  exp(cbind(OR = coef(mylogit), confint(mylogit)))
  
 
```


#Sanity Check on time till start tm start
Quick descriptive to make sure I didnt bungle the regression
```{r}
summarise(group_by(analyze,inpatient),
          mean=mean(time_till,na.rm=TRUE), sd=sd(time_till,na.rm=TRUE))
```

```{r}
source("C:/Users/mdl0193/Documents/test_sg.R")
```




